---
title: "salary_fall22_analysis"
author: "Victoria Stavish"
date: "2022-11-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load libraries

```{r}

library(tidyverse)
library(dplyr)
library(writexl)
library(janitor)
library(readxl)
library(openxlsx)

```

# load data - 10,478 rows

```{r}

data <- read_excel("salary_2022.xlsx") %>% 
  clean_names()

#looking for duplicates - DM
data_dupes <- data %>%
  clean_names() %>% 
  group_by(division, department, title, category_status_cd, category_status, primary_name) %>% 
  summarise(
    count = n()
  ) %>%
  filter(count > 1) %>% 
  left_join(data, by=c("division", "department", "title", "category_status_cd", "category_status", "primary_name")) %>% 
  select(-count)

  

#top 10 highest paid - DM
top_ten_paid_peeps <- data %>% 
  clean_names() %>% 
  arrange(desc(appt_base_annual_salary)) %>% 
  slice(1:10) %>% 
  select(primary_name, appt_base_annual_salary)

write.xlsx(top_ten_paid_peeps, file = 'top_ten_peeps.xlsx')

```

# Work for the bee swarm salary distribution graphics - this is the only graphic that truly contains ALL positions

```{r}

# filter for all positions across all schools to make sure I get 10,478 again

all_positions <- data %>%
  clean_names() %>%
  select(division, title, category_status, category_status_cd, appt_base_annual_salary, primary_name) %>%
  filter(grepl("Tenured Faculty|Tenure Track Faculty|Non-Tenured,Cont. Contr. Faculty|Non-Tenured, Term. Contr. Faculty|Non-Tenured, Non-Regular Faculty|Exempt Regular|Nonexempt Regular|Nonexempt Contingent II|Exempt Contingent II", category_status))


# write that to a cleaner Excel file --> this is the file used for the beeswarm salary distribution graphic
write.xlsx(all_positions, file = 'C:/Users/Vstav/OneDrive/Documents/GitHub/dbk_datadesk/fall22_salary_review/salary_data.xlsx')

```

# median salary overall across all positions and divisions - This is used in the HL of beeswarm distribution graphic
```{r}

median_total <- median(all_positions$appt_base_annual_salary)

```

# The following is work to get the numbers for the donut charts graph - This graphic only contains data for people who work in one of the 12 colleges on campus (AKA not libraries, VP Administration, etc.)

```{r}
# check all the category status types to make sure I'm not missing any
all_categories <- data %>%
  clean_names() %>%
  group_by(category_status) %>%
  count()

# check all the divisions to make sure I'm not missing any
all_divisions <- data %>%
  clean_names() %>%
  group_by(division) %>%
  count()

# dataframe that shows how many of each position exist in each division
positions_in_division <- data %>%
  clean_names() %>%
  group_by(division, category_status) %>%
  count()

# data frame of how many of each positions exist in each college (AKA disclude anything that isn't one of the 12 colleges at this university)
positions_in_colleges <- data %>%
  clean_names() %>%
  filter(!str_detect("Office of the President|Office of Extended Studies|
Libraries|Graduate School|Facilities Management|
Division of Information Technology|Sr VP Academic Affairs & Provost|Undergraduate Studies|Universities at Shady Grove|
VP Administration|VP Finance & CFO|VP Research|VP Student Affairs|VP University Relations", division)) %>%
  group_by(division, category_status) %>%
  count() %>%
  pivot_wider(names_from = category_status, values_from = n)

# write the positions_in_colleges dataframe into an Excel sheet --> this is the Excel sheet used for the donut chart graphic

write.xlsx(positions_in_colleges, file = 'C:/Users/Vstav/OneDrive/Documents/GitHub/dbk_datadesk/fall22_salary_review/position_counts.xlsx')

```
# This is the work to get the median salaries bar charts graphic - This graphic only contains data for people who work in one of the 12 colleges on campus (AKA not libraries, VP Administration, etc.)

# I first found the average salaries of each position in each college, and then the average salary of each position at all colleges overall. I then combined those into one excel sheet

```{r}

#dataframe that shows avg salary of each position at each college

avg_college_pay <- data %>%
  as.data.frame() %>%
  clean_names() %>%
  filter(grepl("Tenured Faculty|Tenure Track Faculty|Non-Tenured,Cont. Contr. Faculty|Non-Tenured, Term. Contr. Faculty|Non-Tenured, Non-Regular Faculty|Exempt Regular|Nonexempt Regular|Nonexempt Contingent II|Exempt Contingent II", category_status)) %>%
  filter(!str_detect("Office of the President|Office of Extended Studies|
Libraries|Graduate School|Facilities Management|
Division of Information Technology|Sr VP Academic Affairs & Provost|Undergraduate Studies|Universities at Shady Grove|
VP Administration|VP Finance & CFO|VP Research|VP Student Affairs|VP University Relations", division)) %>%
  group_by(division, category_status) %>%
  mutate(avg_salary = as.numeric(appt_base_annual_salary)) %>%
  summarise(
    avg_salary = median(appt_base_annual_salary, na.rm=TRUE)
    ) %>%
  pivot_wider(names_from = division, values_from = avg_salary)


```
# avg pay each position overall (discluding admin, libraries, etc.)
```{r}

avg_pay_all <- data %>%
  as.data.frame() %>%
  clean_names() %>%
  filter(grepl("Tenured Faculty|Tenure Track Faculty|Non-Tenured,Cont. Contr. Faculty|Non-Tenured, Term. Contr. Faculty|Non-Tenured, Non-Regular Faculty|Exempt Regular|Nonexempt Regular|Nonexempt Contingent II|Exempt Contingent II", category_status)) %>%
  filter(!str_detect("Office of the President|Office of Extended Studies|
Libraries|Graduate School|Facilities Management|
Division of Information Technology|Sr VP Academic Affairs & Provost|Undergraduate Studies|Universities at Shady Grove|
VP Administration|VP Finance & CFO|VP Research|VP Student Affairs|VP University Relations", division)) %>%
  group_by(category_status) %>%
  mutate(avg_salary = as.numeric(appt_base_annual_salary)) %>%
  summarise(
    avg_salary = median(appt_base_annual_salary, na.rm=TRUE)
  )

# this is me putting both the data frames avg_college_pay and avg_pay_all into an excel sheet. Sheet 1 has all avg salaries by position and college. Sheet 2 has avg salaries by position overall across all 12 colleges. To put this into Flourish, I just copy and pasted the data from Sheet 2 into Sheet 1 to add an 'all' column.

salary_by_division <- list('Sheet1' = avg_college_pay, 'Sheet2' = avg_pay_all)
write.xlsx(salary_by_division, file = 'C:/Users/Vstav/OneDrive/Documents/GitHub/dbk_datadesk/fall22_salary_review/salary_by_division.xlsx')



```

# THIS IS THE END OF WHAT YOU SHOULD NEED TO CHECK THE GRAPHICS

```{r}

```
